### 2016-08-26 section/0_intro.tex
shrink back to 10 pages. will work on threats to validity later

\item Static-dynamic hybrid analysis.
Static analysis alone cannot accurately identify 
inefficiency root causes, because some inefficiency problems only
happen or matter under specific workload. However, pure dynamic analysis will 
cause too large 
run-time overhead. Therefore, we use a hybrid approach to achieve both
performance and accuracy goals.
\end{itemize}

>>>>

\item Static-dynamic hybrid analysis.
Static analysis alone cannot accurately identify 
inefficiency root causes, as some inefficiency only
happens or matters under specific workload; dynamic analysis alone will 
cause too large 
run-time overhead. Therefore, we use a hybrid approach to achieve both
performance and accuracy goals.
\end{itemize}

### 2016-08-26 section/1_under.tex
shrink back to 10 pages. will work on threats to validity later

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true,numbers=left}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
\caption{A resultless 0*1? bug in Mozilla}
\label{fig:Mozilla347306}
\end{figure}

@@

\begin{figure}[t!]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\label{fig:GCC46401}
\end{figure}

@@

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
\caption{A cross-loop redundant bug in Mozilla }
\label{fig:Mozilla477564}
\end{figure}

Intuitively, the above categories above cover many common inefficient
loop problems; each sub-category is concrete enough to guide the design of a
diagnosis tool; none of these (sub-)categories involve application
specific knowledges or heuristics.

>>>>

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true,numbers=left}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla347306.c}}
\caption{A resultless 0*1? bug in Mozilla}
\vspace{-0.05in}
\label{fig:Mozilla347306}
\end{figure}

@@

\begin{figure}[t!]
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/GCC46401.c}}
\caption{A resultless [0$|$1]* bug in GCC }
\vspace{-0.05in}
\label{fig:GCC46401}
\end{figure}

@@

\begin{figure}
\centering
\lstset{basicstyle=\ttfamily\fontsize{8}{8}\selectfont,
     morekeywords={+},keepspaces=true}
  \mbox{\lstinputlisting[mathescape,boxpos=t]{figures/Mozilla477564.js}}
\caption{A cross-loop redundant bug in Mozilla }
\vspace{-0.05in}
\label{fig:Mozilla477564}
\end{figure}

Intuitively, the above categories cover many common inefficient
loop problems; each sub-category is concrete to guide the design of a
diagnosis tool; none of these (sub-)categories involve application
specific knowledges or heuristics.

### 2016-08-26 section/2_workless.tex
shrink back to 10 pages. will work on threats to validity later

\Tool considers two types of instructions as side-effect instructions:
(1) writes to heap or global variables;
(2) writes to a stack variable defined outside the loop and
may be used after the loop.
The second condition is checked through liveness analysis.
\Tool also analyzes all functions called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
\comment{
We consider all calls to library functions or through function pointers 
as having side effects, 
unless the library functions are specially marked by us in a white list.
}
 %to be moved to threats to validity

>>>>

\Tool considers two types of instructions as side-effect instructions:
(1) writes to heap or global variables;
(2) writes to stack variables defined outside the loop and
may be used after the loop (checked through liveness analysis).
\Tool also analyzes all functions called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
\comment{
We consider all calls to library functions or through function pointers 
as having side effects, 
unless the library functions are specially marked by us in a white list.
}
 %to be moved to threats to validity
